Carbon Management Strategies for a Climate-Neutral European Economy

### 2024-01-01 report/submissions/journal/cover_letter/letter.tex
cover letter: correct webiste
incorp Tom review of the cover letter

%%%%%%%%%%%%  Additional Contact Information %%%%%%%%%%%
%
% Set your preferred primary contact address here.
\def\Address{Straße des 17. Juni 135
}
%
\def\CityZip{Berlin, 10623 \\
	Germany}
%
% Set your e-mail here
\def\Email{\textbf{\color{tubred}E-mail}: m.hofmann@tu-berlin.de}
%
% Set your preferred contact number here
%\def\TEL{\textbf{\color{tubred}Tel/Fax}: +86 28 85412720}
%
% Set your department or personal website here
\def\URL{\textbf{\color{tubred}URL}: {https://www.ensys.tu-berlin.de}}
%

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System.” This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes significantly to the critical discourse on climate-neutral energy systems in Europe.

		In our study, we introduce the first large-scale investment model to analyze potential synergies and competition between hydrogen and carbon dioxide transport networks within a carbon-neutral European energy system. Our model represents an advancement over existing models by optimizing a comprehensive range of technologies for the production, transportation, and storage of various energy carriers across all relevant sectors at high temporal and spatial resolution.

>>>>

%%%%%%%%%%%%  Additional Contact Information %%%%%%%%%%%
%
% Set your preferred primary contact address here.
\def\Address{Straße des 17. Juni 135
}
%
\def\CityZip{Berlin, 10623 \\
	Germany}
%
% Set your e-mail here
\def\Email{\textbf{\color{tubred}E-mail}: m.hofmann@tu-berlin.de}
%
% Set your preferred contact number here
%\def\TEL{\textbf{\color{tubred}Tel/Fax}: +86 28 85412720}
%
% Set your department or personal website here
\def\URL{\textbf{\color{tubred}URL}: {https://www.tu.berlin/ensys}}
%

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System.” This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes significantly to the critical discourse on climate-neutral energy systems in Europe.

		In our study, we introduce the first large-scale investment model to analyze potential synergies and competition between hydrogen and carbon dioxide transport networks within a carbon-neutral European energy system. Our model represents an advancement over existing models by optimizing a comprehensive range of technologies for the production, transportation, and storage of of hydrogen and carbon dioxide, along with other energy carriers, across all relevant sectors at high temporal and spatial resolution.
